Pillar 2 - Topic Modeling

### 2019-01-21 Pillar 2 - Topic Modeling.Rmd

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)

@@

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)

@@

## Course Level
```{r tf-idf course, out.height=8, out.width=16, cache = TRUE}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(`Course ID` %in% sample(unique(.$`Course ID`), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = `Course ID`) %>%
                                          group_by(facet) %>%
                                            filter(n >= 2) %>%
                                            top_n(10, tf_idf) %>%
                                          ungroup

@@

  ggsave(paste(id_plot, "beta.jpeg"),
         width = 15, height = 10, path = "Plots")

@@

  ggsave(paste(id_plot, "gamma1.jpeg"),
         width = 15, height = 10, path = "Plots")

@@

  ggsave(paste(id_plot, "gamma2.jpeg"),
         width = 15, height = 10, path = "Plots")

@@

```{r label, eval = F}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))

>>>>

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)

@@

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)

@@

## Course Level
```{r tf-idf course, cache = TRUE}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(`Course ID` %in% sample(unique(.$`Course ID`), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = `Course ID`) %>%
                                          group_by(facet) %>%
                                            filter(n >= 2) %>%
                                            top_n(10, tf_idf) %>%
                                          ungroup

@@

  ggsave(paste(id_plot, "beta.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

@@

  ggsave(paste(id_plot, "gamma1.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

@@

  ggsave(paste(id_plot, "gamma2.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

@@

```{r label, eval = FALSE}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))
